\documentclass[xcolor=dvipsnames, twocolumn]{article}
\usepackage[a4paper]{geometry}
\usepackage{listings}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[utf8]{inputenc}
\usepackage{textpos}
\usepackage{color}
\usepackage{hyperref}
\usepackage[cm]{fullpage}
% \usepackage{showframe}

\lstset{language=D}          % Set your language (you can change the language for each code-block optionally)
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{language=D,
  basicstyle=\ttfamily\scriptsize,
  keywordstyle=\color{blue}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  commentstyle=\color{brown}\ttfamily,
  morecomment=[l][\color{magenta}]{\#}
}

\title{D TODO}
\maketitle

\begin{document}

\section{Emacs and FlyCheck}

\begin{itemize}
\item Highlight q{} in slanted
\item If no errors hide \texttt{*Flycheck errors*} buffer
\item Save should restart current compilation (potentially killing existing).
\item If number of errors change then buffer should be resized using the same
  logic as before.
\end{itemize}

\section{Compiler Diagnostics}
\begin{itemize}

\item pure function 'X' cannot call impure function 'Y', prepend with debug if intentional

\item Better diagnositics when forgetting parentheses in expressions such as

\begin{lstlisting}[frame=single]
b.byLine!(Newline.unix)
\end{lstlisting}

\item Add extra advice for when to use \texttt{.idup} or \texttt{.dup}
  properties when trying to assign/pass a \texttt{mutable T} to an
  \texttt{immutable T}.

This sample diagnostics

\begin{lstlisting}[frame=single]
associative arrays can only be assigned values with immutable keys, not char[]
\end{lstlisting}

should be enhanced with

\begin{lstlisting}[frame=single]
, suffix with .idup if intentional
\end{lstlisting}

\item Add warning flag for casting between mutable, const and immutable.

\item Escape Analysis (EA). Pointers to stack memory should not escape scope. This is
  accepted in unsafe mode but not in safe. (EA) could figure out more
  cases where this should be allowed in safe mode.

See https://en.wikipedia.org/wiki/Escape_analysis

\item Mismatched function calls parameters and unmatched template predicates such as

\begin{lstlisting}[frame=single]
/home/per/Work/justd/geometry.d(553): Error: template instance
  geometry.Vector!(double, 0) does not match template declaration Vector(E, uint
  D, bool normalizedFlag = false, Orient orient = Orient.column) if (D >= 1)
\end{lstlisting}

should only mention the subset of parameters and types that doesn't match such as

\begin{lstlisting}[frame=single]
template parameter D doesn’t fullfil predicate (D >= 1)
\end{lstlisting}

Further, forgetting to include std.functional: binaryFun before doing
\begin{lstlisting}[frame=single]
if (is(typeof(binaryFun!pred(r1.front, r2.front))))
\end{lstlisting}
also gives no hints and can be very deceiving.

\item Detect and warn about duplicate calculations of pure functions (constant
  folding) by adding a SHA1-hash table for all expressions.
\item Better message for mutation of AA members in class constructors or
  functions called from class constructors.

\item Given advice on using template aliases and instatiator functions when
  visible by importes. Probably needs caching.

\item Better message for unguarded AA indexing as
\begin{lstlisting}[frame=single]
auto x= aa[key];
\end{lstlisting}
instead of
\begin{lstlisting}[frame=single]
if (key in aa)
    auto x = aa[key];
\end{lstlisting}

\item Better message for:
\texttt{variable x cannot be read at compile time, use if instead static if (x)}

\item Better diagnostics for
\begin{lstlisting}[frame=single]
auto v = [1,2].ptr[0..\$];
\end{lstlisting}
which currently errors as:
\begin{lstlisting}[frame=single]
Error: undefined identifier __dollar
\end{lstlisting}

\end{itemize}

\section{Compiler Error Handling}

\begin{itemize}
\item Detect duplicates: \texttt{version(print) version(print)}
\end{itemize}

\section{Compiler Inference}

\item Infer \texttt{nothrow}-ness and \texttt{NotNull}-ness for \texttt{hit} in
\begin{lstlisting}[frame=single]
if (key in aa) { auto hit = assumeNotNull(aa[key]); }
\end{lstlisting}
May require key and aa to be immutable. Alternatively wrap result in a Nullable
or catch the exception.

\section{Language}

\begin{itemize}

\item UFCS-syntax for template instantiations.
\begin{lstlisting}[frame=single]
foo!(T,U)
\end{lstlisting}

should equal

\begin{lstlisting}[frame=single]
T.!foo!U
\end{lstlisting}

or

\begin{lstlisting}[frame=single]
T!.foo!U
\end{lstlisting}

\item Turn \texttt{FloatRep} and \texttt{DoubleRep} into either properties or
  template overloads.

\item The cast here should not be necessary:
\begin{lstlisting}[frame=single]
bool x = cast(bool)uniform(0, 2);
\end{lstlisting}

\item Message Passing should move References types if possible (if builtin class
  property r.isUnique returns true) otherwise it copies it using x.dup:
  http://forum.dlang.org/thread/gsvoayxonqyyjlcgfrvs@forum.dlang.org

\item Does D optimize expressions such as
\begin{lstlisting}[frame=single]
string_name == "alpha"
\end{lstlisting}
into only comparing 5 elements?

\item Add keyword for spawning threads/fibers:
\begin{lstlisting}[frame=single]
go f(x);
\end{lstlisting}
instead of current
\begin{lstlisting}[frame=single]
spawn(&f, x);
\end{lstlisting}
similar to Go. See: https://gobyexample.com/goroutines.

\item Perhaps
\item - sync f(x);
\item - async f(x);
\item are good alternatives.

\item Fix better colorization of DDOC CSS templates

\end{itemize}

\begin{itemize}

\item debug-tip: debug writeln inside pure function

\item This segfaults:
\begin{lstlisting}[frame=single]
unittest {
  const x = [1];
  assert(x[] + x[]);
}
\end{lstlisting}
but this gives a clean error
\begin{lstlisting}[frame=single]
unittest {
  const x = [1];
  auto y = x[] + x[];
}
\end{lstlisting}

\item Add Syntax for accessing Template Parameters from Instantiations
\item Copy Rusts Syntax Suger for Pattern matching and Integer Literals such 10i32
\item Only unittest used parts of imported modules. This requires logic that
  figures which unittest that depend on a given function (which is imported).
\item Behaviour of class\_name?.member:
\item null or member.init?
\item When class\_name is null?
\item Just, maybe
\item @nullable
\item Elisp-Style Operators Logical or: Use Operator ??
\item Units:
\item Seems best: http://forum.dlang.org/thread/io1vgo\$1fnc\$1@digitalmars.com
\item
  \texttt{http://forum.dlang.org/thread/mailman.1208.1360603449.22503.digitalmars-d@puremagic.com}
\item \texttt{https://github.com/Arlen/phobos/blob/std\_units/std/units.d}
\item \texttt{https://github.com/klickverbot/phobos/blob/units/std/units.d}
\item \texttt{http://forum.dlang.org/thread/ifo2m5\$19ru\$1@digitalmars.com}
\item Implement “get context at point in file” in DMD similar to what libclang
  does.
\item Add function qualifier attribute @portable ensuring that fundamental
  behaviour will be portable across different target platforms. For example
  function doesn't use

\item range and pointer casts from bytes to shorts etc.
\item unions with

\item std.algorithm.reduce should guess its unit argument based on fun and
  CommonType of input arguments according:
 +, -: 0
 *: 1

\item Forgetting [] should give better error messages in case such as:
  ubyte[20] d; assert(d[].allZeros());

\item Stack-trace for failed unittests or debuggable

\item Accidentically assigning function templates to a variable may give a bit
  cryptic error message: auto x = baseName;

\item User-defined class File together with import std.stdio : File gives no
  intelligent error message.

\item Binary Serialization: Add overloads for to!ubyte[] in std.conv!?

\item Add Warning Flag about Constructor Arguments that shadow struct/class
  members.
\item Improve compiler context feedback for incorrect code in mixins by printing
  the contents of the mixin together with showing were in the mixin the problem
  occurred.
\item Make "Foreach Restrictions" at http://dlang.org/statement.html error in
  compiler
\item Why doesn’t != work for types such as in:
\item if (!is(CommonType!(typeof(min), typeof(max)) == void))
\item Better Error Message for: member function templates with missing extra ()
\item @property pure @safe nothrow real magnitudeSquared() const if
  (isNumeric!E) { … }
\item should be
\item @property pure @safe nothrow real magnitudeSquared()() const if
  (isNumeric!E) { … }
\item DMD is obscure: semicolon expected following function declaration
\item When Comparing Constants String-literals warn about duplicates
\item if-else-if conditions and
\item switch cases
\item Error About Duplicate Conditions if-else-if-chains or switches. May
  require CTFE.
\item Builtin Memoization of Code Generation and Evaluation of Unit Tests and
  Perhaps Also pure functions (Killer App!)
\item Typesafe Use of Index and Slicing using only Unsigned Index Concept:
\item Unsigned
\item Signed
\item Offset:
\item ptr\_t a.ptr
\item Length, Direction
\item ptrdiff\_t d = a.ptr - b.ptr;
\item Point
\item Vector
\item Persistent CTFE Memoization: Requires Compiler + Source Code Hashing
\item Compiler Caching
\item Could be shared of Network
\item Write them on disk so user can see result of CTFE
\item Highlight DDoc Comment Tags and Sections in Emacs for example
\item \$(D alpha)
\item Returns:
\item And Overloads for single character operations on text markings
\item b: Bold
\item i: Italic
\item p: Parameter
\item etc
\item assert and enforce should either capture arguments and their values (say a
  and b) of expressions (say a == b) and print their string values along with
  their values as C++ does with expression templates. Maybe we could use lazy
  here. For ranges it could also what element it fail ed to equal on.
\item Also: My try with assertEqual () and alikes are slower to call than assert
  and cannot be declared safe which is need in struct-local unittests.
\item IDEs such as Eclipse DDT should understand how mixins are expanded and
  make these expandable in the editor
\item /home/per/Work/cognia/bound.d(74): Error: variable Exceptional cannot be
  read at compile time
\item /home/per/Work/cognia/bound.d(74): while looking for match for Bound!(int,
  -2147483648, 2147483647, Exceptional)
\item You need to declare it as immutable.
\item Compiler should
\item Warn about unused imports like Ada for example. This should be easy to
  fix.
\item Warn about unused parameters in non-templated and non-virtual
  functions. Add hint: prepend with cast (void) if intentional
\item Explain why template instantiations with concept requirements doesn’t
  fullfil their needs:
\item For example for opIndex and length needs to be implemented for functions
  that operate RandomAccessRanges for example retro.
\item GCC concepts branch already does this and DMD should be at least as good
  as explaining. If D compiler doesn’t implement it someone else will.
\end{itemize}
\end{document}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
